VM-Centric Snapshot Deduplication for Converged Cloud Architectures

### 2014-07-18 snapshot_system/paper_eval.tex
re

{\bf Settings}.
We have performed a trace-driven study based on a production dataset
from Alibaba Aliyun's cloud platform~\cite{Aliyun} 
with about 2500 VMs, running on 100 physical machines. 
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk.
Each physical machine deals with about 10TB of snapshot data and each 1TB data represents one snapshot version
of 25 VMs.  The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

}
\begin{table}[htb]
\centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline 
&
     \multicolumn{3}{|c|}{VC}  & VO \\ \hline
&
     2\%No PDS &2\%PDS     & 2\%PDS & SRB  \\ 
&        &&     no-simi & \\ \hline
Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
efficiency &          &       &           &      \\    \hline 
Memory(MB) &      46 & 118  & 108 & 2400 \\ \hline
    \end{tabular}
    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}

>>>>

{\bf Settings}.
We have performed a trace-driven study based on a production dataset
from Alibaba Aliyun's cloud platform~\cite{Aliyun} 
with about 2500 VMs, running on 100 physical machines. 
Each machine in the production environment is more powerful than our evaluation cluster
and has 16 cores with 48GB memory.
Each machine hosts up to 25 VMs and each VM keeps 10 automatically-generated snapshots in the storage 
system while a user may instruct extra snapshots to be saved.
Each VM has about 40GB of storage  data  on average
including OS and user data disk while the size distribution is highly skewed and the maximum to
the average ratio is close to 40.
Each physical machine deals with about 10TB of snapshot data and each 1TB data represents one snapshot version
of 25 VMs.  Thus the total amount of raw snapshot shot in 100 physical machines
is about 1,000TB.
The VMs of the sampled data set use popular operating systems such as 
Debian, Ubuntu, Redhat, CentOS, win2008 and win2003. 
%The backup of VM snapshots is required to complete within few  hours every night.
The daily snapshot change rate is about 2-3\% on average.
%All data are divided into 2 MB fix-sized segments and 
The fingerprint for variable-sized chunks is computed using their SHA-1 hash~\cite{similar94,rabin81}. 
%Each segment is divided into 
%variable-sized content chunks with an average size of 4KB.
%Popularity of data blocks are collected through global counting and 
%and top popular ones ($\delta=2\%$)  are  kept in the PDS, as discussed in Section~\ref{sect:store}.

@@

}
\begin{table}[htb]
\centering
    \begin{tabular}{|c|c|c|c|c|}
    \hline 
&
     \multicolumn{3}{|c|}{VC}  & VO \\ \hline
&
     2\%No PDS &2\%PDS     & 2\%PDS & SRB  \\ 
&        &&     no-simi & \\ \hline
Dedup &      93.02\%  & 96.01\% & 94.31\% & 97.86\% \\ 
Efficiency &          &       &           &      \\    \hline 
Memory &      46MB & 118MB  & 108MB & 2.4GB \\ 
per-machine &      &   &  &  \\ \hline
    \end{tabular}
    \caption{Deduplication efficiency and per-machine memory usage for different VC settings and
        Stateless Routing with Binning (SRB).}
    \label{tab:efficiency-comparison}
\end{table}
